Supervised Learning with Fashion MNIST

### 2017-12-13 article/article.tex
article update

\lettrine[nindent=0em,lines=3]{T} he MNIST dataset is considered the "hello world" of Machine Learning.
Current results achieve over 99.7\% accuracy using different techniques
\cite{LWan:2013dg} \cite{DCirean:2012dg} \cite{ISato:2015dg} \cite{JRChang:2015dg} \cite{CYLee:2015dg}.
Also, many good techniques do not work well on this dataset because of its simplicity \cite{CFran:2017dg}.
Because of this, many consider this an improper

@@

>>>>

\lettrine[nindent=0em,lines=3]{T} he MNIST dataset is considered the "hello world" of Machine Learning.
Current results achieve over 99.7\% accuracy using different techniques
\cite{LWan:2013dg} \cite{DCirean:2012dg} \cite{ISato:2015dg} \cite{JRChang:2015dg} \cite{CYLee:2015dg}.
Also, many good techniques do not work well on this dataset because of its simplicity \cite{CFran:2017dg}.
With that in mind, the Fashion MNIST dataset \cite{FashionMNIST} was created. It has same size and format
of the MNIST dataset (70.000 grayscale images of size 28x28 labeled into 10 different classes) meaning that
it should be as simple to use, but its images consist of fashion items which are supposedly harder to
classify.

The goal of this work is to explore different techniques of supervised learning for classifying the images
in the Fashion MNIST dataset. We want to measure the accuracy of our tests and compare them with different
results on the same dataset, while also trying to obtain some intuition behind the data.

\section{Preparation}

The Fashion MNIST is already subdivided into two sets. A set of 60.000 images (the training set)
and a set of 10.000 images (the test set). The idea is to learn with the training set and then
evaluate the performance of our trained model with the test set.

We will be using the standard accuracy as a metric for our tests:
\begin{equation}
\label{eq:acc}
accuracy = \frac{\#(correct\_classifications)}{\#(test\_set\_size)}
\end{equation}

The dataset is already provided as a list of (28*28)+1 sized vectors corresponding
to each of the 28*28 pixels of the image plus 1 entry for the classification.
Since each pixel value was an integer from 0 to 255, we have opted to divide
each value by 255 to achieve features that goes from 0 to 1.

\section{Known Results}

The Fashion MNIST repository contains some benchmarks using the python library
scikit-learn \cite{scikitlearn} \cite{scikitlearnbenchmark}. They are not meant
to be efficient or good, but they work as a baseline for our project.
The best result (corresponding to the best selection of parameters tested)
of each algorithm are displayed in table \ref{table:scikit-benchmark}.

\begin{table}
\centering
\begin{tabular}{llr}
\toprule
Algorithm Name & Best Accuracy (\%) \\
\midrule
SVC & $89.7$ \\
Gradient Boosting & $88.8$ \\
Random Forest & $87.9$ \\
MLP & $87.7$ \\
K-Neighbors & $86.0$ \\
Logistic Regression & $84.0$ \\
SGD & $82.9$ \\
Decision Tree & $80.1$ \\
\bottomrule
\end{tabular}
\caption{Fashion MNIST Scikit-Learn Benchmark \cite{scikitlearnbenchmark} }
\label{table:scikit-benchmark}
\end{table}

The current state of art for the Fashion MNIST dataset is a recent one, with 96.3\% accuracy using Wide
Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper}.
We will consider this as the ceiling accuracy for our project.

@@

\bibitem{FashionMNIST}
Fashion-MNIST: a Novel Image Dataset for Benchmarking Machine Learning Algorithms. Han Xiao, Kashif Rasul, Roland Vollgraf

\bibitem{scikitlearn}
API design for machine learning software: experiences from the scikit-learn project, Buitinck et al., 2013

\bibitem{scikitlearnbenchmark}
Zalando Research. Fashion MNIST Scikit-Learn benchmark. http://fashion-mnist.s3-website.eu-central-1.amazonaws.com/

\bibitem{randomerasingdataaugmentationpaper}
Zhong Z., Zheng L., Kang G., Li S., Yang Y. . Random Erasing Data Augmentation. ArXiv e-prints 1708.04896 2017
